Early life telomere dynamics

### 2015-06-22 Talks/Warbler meeting December 2014.Rmd
First upload of all data and scripts

---
output:
  beamer_presentation:
    fig_caption: yes
    colortheme: 'dove'
---

```{r load clean, include = FALSE}
#Load and clean data
rm(list=ls())
setwd('..')
source('Scripts/SW juvenile telomeres IPC load.r')
source('Scripts/SW juvenile telomeres IPC functions.r')
source('Scripts/SW juvenile telomeres IPC clean.r')

@@

## **In early life?**

@@

@@

@@

####Model including only juvenile birds (*N* = `r nrow(juv)`)

```{r, eval = FALSE}
mymodel <- lm(Telomere_Length ~ Mass + 
                                Tarsus_Length + 
                                Age_Class + 
                                Sex + 
                                Territory_Quality + 
                                EPP + 
                                Helper,
              data = juveniles)
```

@@

@@

@@

## **Thanks!**

- Pat Monaghan
- Winnie Boner
- Simon Verhulst

**Seychelles warbler study group**  (*Emma Barrett*, Jan Komdeur, Terry Burke and all the other warbler researchers)

\begin{center}
  \includegraphics{Pictures/UEAlogo.png}
\end{center}

\begin{center}
  \includegraphics{Pictures/NERClogo.png}
\end{center}

>>>>

---
title: "Early life telomere dynamics"
author: "Lewis Spurgin"
date: "December 2014"
output: beamer_presentation
---

```{r load clean, include = FALSE}
#Load and clean data
rm(list=ls())
setwd('..')
source('Scripts/SW juvenile telomeres IPC load.r')
source('Scripts/SW juvenile telomeres IPC functions.r')
source('Scripts/SW juvenile telomeres IPC clean v2.r')

@@

##Late life consequences of early life experiences
\begin{center}
  \includegraphics{Pictures/BrouwerFig.png}
\end{center}

##Telomeres as biomarkers of early life costs
\begin{center}
  \includegraphics{Pictures/HeidingerFig.png}
\end{center}

@@

## **Data**
- Juvenile birds caught between 1997-2000 (plus a few later ones)

- Mostly Dead

- *N* = `r nrow(juv)`

@@

tapply(juv$LogTL,list(juv$EPP,juv$Sex),length)

@@

@@

## **What factors affect telomere length in early life?**
```{r, echo=FALSE,fig.height=4,fig.width=8, fig.cap='Telomere length and EPP * Age'}
layout(matrix(1:2,1,2))
par(mar = c(5,5,2,0))
errorplot(y = juvHelp$TLKB,
          x = juvHelp$Ageclass,
          myylab = 'Telomere Length (kb)',
          myxlab = 'Age Class',
          mymain = 'Helpers present',
          myylim = c(4.5,7),
          myxlim <- c(0,1))

par(mar=c(5,3,2,2))
errorplot(y = juvNotHelp$TLKB,
          x = juvNotHelp$Ageclass,
          myylab = '',
          myxlab = 'Age Class',
          mymain = 'Helpers absent',
          myylim = c(4.5,7),
          myxlim <- c(0,1))
```

@@

##Telomeres as biomarkers of early life costs
\begin{center}
  \includegraphics{Pictures/BoonekampFig.png}
\end{center}

@@
